---
title: "Propensity Score Analysis"
output: html_notebook
---
We usually estimate treatment effect through randomized experiment where there is a control group and a experimental group. However it is often the case that treatments were not randomly assigned to subjects. 

## Data Exploring
```{r}
data <- read.csv("http://web.hku.hk/~bcowling/data/propensity.csv", header=TRUE)
data$death = as.factor(data$death)
data$trt = as.factor(data$trt)
data
```

### Check randomness
```{r}
library(ggplot2)
ggplot(data, aes(x=age, y=..density..))  +
  geom_histogram(aes( fill=trt, color=trt), bins =30 ) +
  geom_density() +
  facet_grid(.~ trt)
```
From the plot above, we observed that people in treatment group (trt = 1) were slightly older than those in control group.


```{r}
ggplot(data,aes(x=risk, fill=trt)) +  
  geom_bar(position = 'identity') +
  facet_grid(.~ trt)
```


```{r}
ggplot(data,aes(x=severity, fill=trt)) +
  geom_bar(position = 'identity') +
  facet_grid(.~ trt)
```

Based on the plots above, it's not hard to observe that the distributions of few varaibles are not the same across two g
